Data Description
```{r}
options(digits = 3, scipen = 50)
library(car)
library(caret)
library(dplyr)
```

# The data is read using the read.csv() function.The first six pieces of data are then displayed using the head()v function.
```{r}
df <- read.csv("~/Downloads/Life Expectancy Data.csv", header=T)
head(df)
```

# Add a new variable DEVELOPED.Use the str () function to display data structure information
```{r}
df$developed <- ifelse(df$Status == "Developing", 0, 1)
str(df)
```
```{r}
write.csv(df, file = "df.csv", row.names = F)
```


# We have Country, Year, Status, developed as factor variable,
# When plotting and calculating the correlation coefficient, it is necessary to eliminate the value range of each variable among the remaining numerical variables is quite different,
# The data needs to be standardized.
```{r}
df1 <- df[, -c(1, 2, 3, 23)]
stand_scale <- preProcess(df1)
df2 <- na.omit(predict(stand_scale, df1))
head(df2)
```

# Using the cor () function to calculate the correlation coefficient matrix between the variables, the results are shown below.
```{r}
result.cor <- round(cor(df2), 2)
result.cor
```

# According to the above correlation coefficient results, variables with correlation coefficient greater than 0.7 are screened to draw a scatter plot matrix
```{r}
result.cor1 <- result.cor
result.cor1[result.cor1 < 0.7] <- "N"
result.cor1[result.cor == 1] <- "N"
result.cor1
a <- c("GDP", "Income.composition.of.resources", "Schooling",  "Life.expectancy", "percentage.expenditure", 
       "thinness..1.19.years", "thinness.5.9.years")
df3 <- df1[, a]
scatterplotMatrix(df3, spread = FALSE, smoother.args = list(lty = 2), 
                  main = "Scatter Plot Matrix")
```
Method
```{r}
Life.Expectancy.Data <- read.csv("~/Downloads/Life Expectancy Data.csv", header=T)
```
Using Backward model selection method
life expectancy is y, other 18 indictors are variables
```{r}
lm(Life.expectancy~ 
Adult.Mortality+
infant.deaths+
Alcohol+
percentage.expenditure+
Hepatitis.B+
Measles+
 BMI +
under.five.deaths +
Polio+
Total.expenditure+
Diphtheria+ 
 HIV.AIDS+
GDP+
Population+
 thinness..1.19.years+
 thinness.5.9.years+
Income.composition.of.resources+
Schooling, data=Life.Expectancy.Data)
```
Lets define the alpha out equal to 0.05
summary will show the p-value for each variable.
```{r}
summary(lm(Life.expectancy~ 
Adult.Mortality+
infant.deaths+
Alcohol+
percentage.expenditure+
Hepatitis.B+
Measles+
 BMI +
under.five.deaths +
Polio+
Total.expenditure+
Diphtheria+ 
 HIV.AIDS+
GDP+
Population+
 thinness..1.19.years+
 thinness.5.9.years+
Income.composition.of.resources+
Schooling, data=Life.Expectancy.Data))
```
In table we can see the thinness..1.19.years with the largest p-vlaue and larger than alpha out, so we delete it.
```{r}
lm(Life.expectancy~ 
Adult.Mortality+
infant.deaths+
Alcohol+
percentage.expenditure+
Hepatitis.B+
Measles+
 BMI +
under.five.deaths +
Polio+
Total.expenditure+
Diphtheria+ 
 HIV.AIDS+
GDP+
Population+
thinness.5.9.years+
Income.composition.of.resources+
Schooling, data=Life.Expectancy.Data)
```

```{r}
summary(lm(Life.expectancy~ 
Adult.Mortality+
infant.deaths+
Alcohol+
percentage.expenditure+
Hepatitis.B+
Measles+
 BMI +
under.five.deaths +
Polio+
Total.expenditure+
Diphtheria+ 
 HIV.AIDS+
GDP+
Population+
thinness.5.9.years+
Income.composition.of.resources+
Schooling, data=Life.Expectancy.Data))
```
In the table In table we can see the population with the largest p-vlaue and larger than alpha out, so we delete it.
```{r}
lm(Life.expectancy~ 
Adult.Mortality+
infant.deaths+
Alcohol+
percentage.expenditure+
Hepatitis.B+
Measles+
 BMI +
under.five.deaths +
Polio+
Total.expenditure+
Diphtheria+ 
 HIV.AIDS+
GDP+
thinness.5.9.years+
Income.composition.of.resources+
Schooling, data=Life.Expectancy.Data)
```

```{r}
summary(lm(Life.expectancy~ 
Adult.Mortality+
infant.deaths+
Alcohol+
percentage.expenditure+
Hepatitis.B+
Measles+
 BMI +
under.five.deaths +
Polio+
Total.expenditure+
Diphtheria+ 
 HIV.AIDS+
GDP+
thinness.5.9.years+
Income.composition.of.resources+
Schooling, data=Life.Expectancy.Data))
```
In table we can see the Hepatitis.B with the largest p-vlaue and larger than alpha out, so we delete it.
```{r}
lm(Life.expectancy~ 
Adult.Mortality+
infant.deaths+
Alcohol+
percentage.expenditure+
Measles+
 BMI +
under.five.deaths +
Polio+
Total.expenditure+
Diphtheria+ 
 HIV.AIDS+
GDP+
thinness.5.9.years+
Income.composition.of.resources+
Schooling, data=Life.Expectancy.Data)
```

```{r}
summary(lm(Life.expectancy~ 
Adult.Mortality+
infant.deaths+
Alcohol+
percentage.expenditure+
Measles+
BMI +
under.five.deaths +
Polio+
Total.expenditure+
Diphtheria+ 
 HIV.AIDS+
GDP+
thinness.5.9.years+
Income.composition.of.resources+
Schooling, data=Life.Expectancy.Data))
```
In table we can see the Alcohol with the largest p-vlaue and larger than alpha out, so we delete it.
```{r}
lm(Life.expectancy~ 
Adult.Mortality+
infant.deaths+
percentage.expenditure+
Measles+
 BMI +
under.five.deaths +
Polio+
Total.expenditure+
Diphtheria+ 
 HIV.AIDS+
GDP+
thinness.5.9.years+
Income.composition.of.resources+
Schooling, data=Life.Expectancy.Data)
```

```{r}
summary(lm(Life.expectancy~ 
Adult.Mortality+
infant.deaths+
percentage.expenditure+
Measles+
 BMI +
under.five.deaths +
Polio+
Total.expenditure+
Diphtheria+ 
 HIV.AIDS+
GDP+
thinness.5.9.years+
Income.composition.of.resources+
Schooling, data=Life.Expectancy.Data))
```
In table we can see the Total.expenditure with the largest p-vlaue and larger than alpha out, so we delete it.
```{r}
lm(Life.expectancy~ 
Adult.Mortality+
infant.deaths+
percentage.expenditure+
Measles+
 BMI +
under.five.deaths +
Polio+
Diphtheria+ 
 HIV.AIDS+
GDP+
thinness.5.9.years+
Income.composition.of.resources+
Schooling, data=Life.Expectancy.Data)
```

```{r}
summary(lm(Life.expectancy~ 
Adult.Mortality+
infant.deaths+
percentage.expenditure+
Measles+
 BMI +
under.five.deaths +
Polio+
Diphtheria+ 
 HIV.AIDS+
GDP+
thinness.5.9.years+
Income.composition.of.resources+
Schooling, data=Life.Expectancy.Data))
```
In table we can see the Measles with the largest p-vlaue and larger than alpha out, so we delete it.
```{r}
lm(Life.expectancy~ 
Adult.Mortality+
infant.deaths+
percentage.expenditure+
 BMI +
under.five.deaths +
Polio+
Diphtheria+ 
 HIV.AIDS+
GDP+
thinness.5.9.years+
Income.composition.of.resources+
Schooling, data=Life.Expectancy.Data)
```

```{r}
summary(lm(Life.expectancy~ 
Adult.Mortality+
infant.deaths+
percentage.expenditure+
 BMI +
under.five.deaths +
Polio+
Diphtheria+ 
 HIV.AIDS+
GDP+
thinness.5.9.years+
Income.composition.of.resources+
Schooling, data=Life.Expectancy.Data))
```
In this table we can see every variables are less than alpha out vlaue and all of them are significant variables. Therefore we can get the final model y=52.4025809-0.0166069x1+0.0873726x2+0.0001801x4+0.0327984x7-0.0650677x8+ 0.0213506x9+0.0256096x11-0.4740475x12+0.0000314x13-0.0922148x16+7.4856404x17+0.8945372x18+e
```{r}
AIC(lm(Life.expectancy~ 
Adult.Mortality+
infant.deaths+
percentage.expenditure+
 BMI +
under.five.deaths +
Polio+
Diphtheria+ 
 HIV.AIDS+
GDP+
thinness.5.9.years+
Income.composition.of.resources+
Schooling, data=Life.Expectancy.Data))
```
The AIC for this model is 13588.39
```{r}
plot(lm(Life.expectancy~ 
Adult.Mortality+
infant.deaths+
percentage.expenditure+
 BMI +
under.five.deaths +
Polio+
Diphtheria+ 
 HIV.AIDS+
GDP+
thinness.5.9.years+
Income.composition.of.resources+
Schooling, data=Life.Expectancy.Data))
```
In Residual vs Fittied every circles show the every single error，the vast majority of errors distribute around E(ei)=0, in Normall Q-Q plot we can see this final model is in accordance with normal distribution,  Scale-Location shows every variance of residual almost equal, and Residuals vs Leverage shows no abnormal points in the final model
